Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

>>>>

Therefore, the workflow that must be carried out by the performance regression analysis (PRA) system is as follows:
\begin{enumerate}
	\item The system must be able to detect when there is a regression in Microservice-based applications
	\item The system must be able to determine the source or root cause of the regression after it is detected
\end{enumerate}\textbf{}
